

\chapter[校园生活]{校园生活}
\label{cp:user-guide}

{
\parindent2pt

\indent 
\noindent\hspace{2em}这一章节会对科大的校园生活做出一些简要介绍，帮助大家熟悉各类基础设施的分布以及在这里你所享受的福利待遇


% \begin{verbatim}
% 00-Abstract.tex
% 01-Introduction.tex
% 02-User-Guide.tex
% ...
% \end{verbatim}


\section{校园基础设施}
Although this template is specifically tailored for students from all six schools of the Polytechnic University of Leiria, you are welcome to use it if you are from a different institution. It is highly customisable and can be easily modified to suit the needs of other schools. If your school is interested in adopting this as the official template, please contact me first. Although this template is specifically tailored for students from all six schools of the Polytechnic University of Leiria, you are welcome to use it if you are from a different institution. It is highly customisable and can be easily modified to suit the needs of other schools. If your school is interested in adopting this as the official template, please contact me first. Although this template is specifically tailored for students from all six schools of the Polytechnic University of Leiria, you are welcome to use it if you are from a different institution. It is highly customisable and can be easily modified to suit the needs of other schools. If your school is interested in adopting this as the official template, please contact me first. Although this template is specifically tailored for students from all six schools of the Polytechnic University of Leiria, you are welcome to use it if you are from a different institution. It is highly customisable and can be easily modified to suit the needs of other schools. If your school is interested in adopting this as the official template, please contact me first. 